---
title: "analysis"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load packages and data
```{r}
# packages
library(pacman)
pacman::p_load(
  brms,
  tidyverse,
  bayesplot,
  viridis,
  data.table,
  ggplot2,
  BayesCombo,
  patchwork,
  beepr,
  graphics,
  lmerTest,
  loo,
  rlist,
  bayestestR,
  tidybayes,
  ggridges
)

# load data
df <- read_csv("data/finaldata_18_11_2020.csv")
df$X1 <- NULL

# # tests
# test <- df %>% subset(feature == "pitch_variability") %>% 
#   group_by(expt_unique_disorder, dis_task) %>%
#   summarise(n = n())

```

Possible features
```{r}

#possible features: at least 3 disorders, where each has data from at least 5 studies
features <- data %>%
  group_by(disorder, feature) %>%
  summarise(n_studies = n(), .groups = "drop_last") %>%
  filter(n_studies >= 5)

possible_features <- features %>%
  group_by(feature) %>%
  summarise(n_disorder = n(), .groups = "drop_last",
            disorders = list(disorder)) %>%
  filter(n_disorder >= 3)

```

Define Functions
```{r}

# subset for voice feature
feature_subset <- function(dataset, feature_name) {
  invisible(
    subset(dataset, feature == feature_name) %>%
    group_by(disorder) %>%
    filter(n() >= 5))
  
}

# run models (can be used for prior and real model)
brm_fit <- function(def_formula, data_subset, def_priors, sample_prior) {
  if (sample_prior == "only"){
    model <- brm(
      formula = def_formula,
      data = data_subset,
      family = student(),
      prior = def_priors,
      sample_prior = "only",
      seed = 28,
      chains = 4,
      cores = 3,
      iter = 4000,
      control = list(
        max_treedepth = 20,
        adapt_delta=0.98))
  }
  if (sample_prior == T) {
    model <- brm(
      formula = def_formula,
      data = data_subset,
      family = student(),
      prior = def_priors,
      sample_prior = T,
      seed = 28,
      chains = 4,
      cores = 3,
      iter = 4000,
      control = list(
        max_treedepth = 20,
        adapt_delta=0.98))
  }
  return(model)
}

# complete function, running models
complete_brms <- function(data, feature, formula, priors, loo_criterion) {
  
  subset <- feature_subset(dataset = data, feature_name = feature) 
  prior_model <- brm_fit(def_formula = formula, data_subset = subset, def_priors = priors, sample_prior = "only")
  posterior_model <- brm_fit(def_formula = formula, data_subset = subset, def_priors = priors, sample_prior = T)
  pp_checks <- pp_check(prior_model, nsamples = 1000) + pp_check(posterior_model, nsamples = 1000)
  summary <- summary(posterior_model)
  mcmc_trace <- mcmc_trace(posterior_model) + theme_classic()
  mcmc_rank <- mcmc_rank_overlay(posterior_model) + theme_classic()
  
  if (loo_criterion == T){
    posterior_model <- add_criterion(posterior_model, criterion = "loo", reloo = T, seed = TRUE)}
  
  return_objects <- list("data" = subset,
                         "feature" = feature, 
                         "prior_model" = prior_model,
                         "posterior_model" = posterior_model,
                         "pp_checks" = pp_checks,
                         "posterior_summary" = summary,
                         "mcmc_trace" = mcmc_trace, 
                         "mcmc_rank" = mcmc_rank)
  
  return(return_objects)
}

```

Define Formulas and Priors
```{r}

# formulas
f_disorder <- bf(g_calc | se(g_var_calc) ~ 0 + disorder + 
                   (1|gr(same_sample, by = disorder)) + (1|gr(study_disorder, by = disorder)) + (1|gr(expt_unique_dis, by = disorder)))

f_task <- bf(g_calc | se(g_var_calc) ~ 0 + disorder:task_type + 
               (1|gr(same_sample, by = disorder)) + (1|gr(study_disorder, by = disorder)) + (1|gr(expt_unique_dis, by = dis_task)))

f_lang <- bf(g_calc | se(g_var_calc) ~ 0 + disorder:native_language + 
               (1|gr(same_sample, by = dis_lang)) + (1|gr(study_disorder, by = disorder)) + (1|gr(expt_unique_dis, by = dis_lang)))
       
# priors
model_priors <- c(prior(normal(0, 2.5), class = b))

```

Run Models with all data (for hypothesis testing and to find out which are problematic), and save them
```{r}

# pause duration #
brm_pd_disorder <- complete_brms(data = df, feature = "pause_duration", formula = f_disorder, priors = model_priors, loo_criterion = F)
saveRDS(brm_pd_disorder, "envr/brm_pd_disorder_2020_20_11.rds")
brm_pd_task <- complete_brms(data = df, feature = "pause_duration", formula = f_task, priors = model_priors, loo_criterion = F) 
saveRDS(brm_pd_task, "envr/brm_pd_task_2020_20_11.rds")
brm_pd_lang <- complete_brms(data = df, feature = "pause_duration", formula = f_lang, priors = model_priors, loo_criterion = F)
saveRDS(brm_pd_lang, "envr/brm_pd_lang_2020_20_11.rds")

# pitch #
brm_pi_disorder <- complete_brms(data = df, feature = "pitch", formula = f_disorder, priors = model_priors, loo_criterion = F)
saveRDS(brm_pi_disorder, "envr/brm_pi_disorder_2020_20_11.rds")
brm_pi_task <- complete_brms(data = df, feature = "pitch", formula = f_task, priors = model_priors, loo_criterion = F) 
saveRDS(brm_pi_task, "envr/brm_pi_task_2020_20_11.rds")
brm_pi_lang <- complete_brms(data = df, feature = "pitch", formula = f_lang, priors = model_priors, loo_criterion = F) 
saveRDS(brm_pi_lang, "envr/brm_pi_lang_2020_20_11.rds")

# pitch variability #
brm_pv_disorder <- complete_brms(data = df, feature = "pitch_variability", formula = f_disorder, priors = model_priors, loo_criterion = F) 
saveRDS(brm_pv_disorder, "envr/brm_pv_disorder_2020_20_11.rds")
brm_pv_task <- complete_brms(data = df, feature = "pitch_variability", formula = f_task, priors = model_priors, loo_criterion = F) 
saveRDS(brm_pv_task, "envr/brm_pv_task_2020_20_11.rds")
brm_pv_lang <- complete_brms(data = df, feature = "pitch_variability", formula = f_lang, priors = model_priors, loo_criterion = F)
saveRDS(brm_pv_lang, "envr/brm_pv_lang_2020_20_11.rds")
  
```

Quality checks: pause duration
```{r}

# get unique values
unique(brm_pd_disorder$data$disorder) # scz, lhd, rhd

# disorder #
parnames(brm_pd_disorder$posterior_model)
# summary
brm_pd_disorder$posterior_summary
# mcmc_checks 
brm_pd_disorder$mcmc_trace  
brm_pd_disorder$mcmc_rank
# pretty mcmcm for paper: 1100x350
color_scheme_set("viridis")
mcmc_trace(brm_pd_disorder$posterior_model, pars = vars(-contains("["), -contains("prior"), -contains("lp"), -contains("sigma"))) + theme_classic()
mcmc_rank_overlay(brm_pd_disorder$posterior_model, pars = vars(-contains("["), -contains("prior"), -contains("lp"), -contains("sigma"))) + theme_classic()
# pp_checks 
brm_pd_disorder$pp_checks
# b: absolute values (effect sizes)
plot(hypothesis(brm_pd_disorder$posterior_model,"disorderlhd = 0"))
plot(hypothesis(brm_pd_disorder$posterior_model,"disorderrhd = 0"))
plot(hypothesis(brm_pd_disorder$posterior_model,"disorderscz = 0"))
# sd for same sample
plot(hypothesis(brm_pd_disorder$posterior_model, "Intercept:disorderlhd = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pd_disorder$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pd_disorder$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "same_sample"))
# sd for study_disorder
plot(hypothesis(brm_pd_disorder$posterior_model, "Intercept:disorderlhd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pd_disorder$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pd_disorder$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "study_disorder"))
# sd for expt unique
plot(hypothesis(brm_pd_disorder$posterior_model, "Intercept:disorderlhd = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pd_disorder$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pd_disorder$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "expt_unique_dis"))
#nu
plot(hypothesis(brm_pd_disorder$posterior_model, "nu = 0", class = ""))

# task type #
parnames(brm_pd_task$posterior_model)
# summary
brm_pd_task$posterior_summary
# mcmc_checks 
brm_pd_task$mcmc_trace  
brm_pd_task$mcmc_rank
# pretty mcmcm for paper in 1000x600
color_scheme_set("viridis")
mcmc_trace(brm_pd_task$posterior_model, pars = vars(-contains("["), -contains("prior"), -contains("lp"), -contains("sigma"))) + theme_classic()
mcmc_rank_overlay(brm_pd_task$posterior_model, pars = vars(-contains("["), -contains("prior"), -contains("lp"), -contains("sigma"))) + theme_classic()
# pp_checks 
brm_pd_task$pp_checks
# b
plot(hypothesis(brm_pd_task$posterior_model,"disorderlhd:task_typeconstrainedproduction = 0"))
plot(hypothesis(brm_pd_task$posterior_model,"disorderrhd:task_typeconstrainedproduction = 0"))
plot(hypothesis(brm_pd_task$posterior_model,"disorderscz:task_typeconstrainedproduction = 0"))
plot(hypothesis(brm_pd_task$posterior_model,"disorderscz:task_typefreemonologicalproduction = 0"))
plot(hypothesis(brm_pd_task$posterior_model,"disorderscz:task_typesocialinteraction = 0"))
# sd for same_sample
plot(hypothesis(brm_pd_task$posterior_model, "Intercept:disorderlhd = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pd_task$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pd_task$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "same_sample"))
# sd for study_disorder
plot(hypothesis(brm_pd_task$posterior_model, "Intercept:disorderlhd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pd_task$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pd_task$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "study_disorder"))
# sd for expt_unqiue_dis
plot(hypothesis(brm_pd_task$posterior_model, "Intercept:dis_tasklhd_constrainedproduction = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pd_task$posterior_model, "Intercept:dis_taskrhd_constrainedproduction = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pd_task$posterior_model, "Intercept:dis_taskscz_constrainedproduction = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pd_task$posterior_model, "Intercept:dis_taskscz_freemonologicalproduction = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pd_task$posterior_model, "Intercept:dis_taskscz_socialinteraction = 0", class = "sd", group = "expt_unique_dis"))
#nu
plot(hypothesis(brm_pd_task$posterior_model, "nu = 0", class = ""))

# language #
parnames(brm_pd_lang$posterior_model)
# summary
brm_pd_lang$posterior_summary
# mcmc_checks 
brm_pd_lang$mcmc_trace  
brm_pd_lang$mcmc_rank
# pretty mcmcm for paper in 1400x500
color_scheme_set("viridis")
mcmc_trace(brm_pd_lang$posterior_model, pars = vars(-contains("["), -contains("prior"), -contains("lp"), -contains("sigma"))) + theme_classic()
mcmc_rank_overlay(brm_pd_lang$posterior_model, pars = vars(-contains("["), -contains("prior"), -contains("lp"), -contains("sigma"))) + theme_classic()
# pp_checks 
brm_pd_lang$pp_checks
# b
plot(hypothesis(brm_pd_lang$posterior_model,"disorderlhd:native_languageEnglish = 0"))
plot(hypothesis(brm_pd_lang$posterior_model,"disorderrhd:native_languageEnglish = 0"))
plot(hypothesis(brm_pd_lang$posterior_model,"disorderscz:native_languageEnglish = 0"))
plot(hypothesis(brm_pd_lang$posterior_model,"disorderscz:native_languageGerman = 0")) 
plot(hypothesis(brm_pd_lang$posterior_model,"disorderlhd:native_languageKorean = 0"))
plot(hypothesis(brm_pd_lang$posterior_model,"disorderrhd:native_languageKorean = 0"))
# sd for same_sample
plot(hypothesis(brm_pd_lang$posterior_model, "Intercept:dis_langlhd_English = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pd_lang$posterior_model, "Intercept:dis_langlhd_Korean = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pd_lang$posterior_model, "Intercept:dis_langrhd_English = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pd_lang$posterior_model, "Intercept:dis_langrhd_Korean = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pd_lang$posterior_model, "Intercept:dis_langscz_English = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pd_lang$posterior_model, "Intercept:dis_langscz_German = 0", class = "sd", group = "same_sample"))
# sd for study_disorder
plot(hypothesis(brm_pd_lang$posterior_model, "Intercept:disorderlhd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pd_lang$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pd_lang$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "study_disorder"))
# sd for expt_unique
plot(hypothesis(brm_pd_lang$posterior_model, "Intercept:dis_langlhd_English = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pd_lang$posterior_model, "Intercept:dis_langlhd_Korean = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pd_lang$posterior_model, "Intercept:dis_langrhd_English = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pd_lang$posterior_model, "Intercept:dis_langrhd_Korean = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pd_lang$posterior_model, "Intercept:dis_langscz_English = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pd_lang$posterior_model, "Intercept:dis_langscz_German = 0", class = "sd", group = "expt_unique_dis"))
#nu
plot(hypothesis(brm_pd_lang$posterior_model, "nu = 0", class = ""))

```

Quality checks: pitch
```{r}

# get unique values
unique(brm_pi_disorder$data$disorder) # asd, rhd, scz

# disorder #
parnames(brm_pi_disorder$posterior_model)
# summary
brm_pi_disorder$posterior_summary
# mcmc_checks 
brm_pi_disorder$mcmc_trace  
brm_pi_disorder$mcmc_rank
# pretty mcmcm for paper in 1000x600
color_scheme_set("viridis")
mcmc_trace(brm_pi_disorder$posterior_model, pars = vars(-contains("["), -contains("prior"), -contains("lp"), -contains("sigma"))) + theme_classic()
mcmc_rank_overlay(brm_pi_disorder$posterior_model, pars = vars(-contains("["), -contains("prior"), -contains("lp"), -contains("sigma"))) + theme_classic()
# pp_checks 
brm_pi_disorder$pp_checks
# b: absolute values (effect sizes)
plot(hypothesis(brm_pi_disorder$posterior_model,"disorderasd = 0"))
plot(hypothesis(brm_pi_disorder$posterior_model,"disorderrhd = 0"))
plot(hypothesis(brm_pi_disorder$posterior_model,"disorderscz = 0"))
# sd for same sample
plot(hypothesis(brm_pi_disorder$posterior_model, "Intercept:disorderasd = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pi_disorder$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pi_disorder$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "same_sample"))
# sd for study_disorder
plot(hypothesis(brm_pi_disorder$posterior_model, "Intercept:disorderasd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pi_disorder$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pi_disorder$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "study_disorder"))
# sd for study_disorder
plot(hypothesis(brm_pi_disorder$posterior_model, "Intercept:disorderasd = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pi_disorder$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pi_disorder$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "expt_unique_dis"))
# nu
plot(hypothesis(brm_pi_disorder$posterior_model, "nu = 0", class = ""))

# task #
parnames(brm_pi_task$posterior_model)
# summary
brm_pi_task$posterior_summary
# mcmc_checks 
brm_pi_task$mcmc_trace  
brm_pi_task$mcmc_rank
# pretty mcmcm for paper in 1000x600
color_scheme_set("viridis")
mcmc_trace(brm_pi_task$posterior_model, pars = vars(-contains("["), -contains("prior"), -contains("lp"), -contains("sigma"))) + theme_classic()
mcmc_rank_overlay(brm_pi_task$posterior_model, pars = vars(-contains("["), -contains("prior"), -contains("lp"), -contains("sigma"))) + theme_classic()
# pp_checks 
brm_pi_task$pp_checks
# b
plot(hypothesis(brm_pi_task$posterior_model,"disorderasd:task_typefreemonologicalproduction = 0"))
plot(hypothesis(brm_pi_task$posterior_model,"disorderasd:task_typesocialinteraction = 0"))
plot(hypothesis(brm_pi_task$posterior_model,"disorderrhd:task_typeconstrainedproduction = 0"))
plot(hypothesis(brm_pi_task$posterior_model,"disorderscz:task_typeconstrainedproduction = 0"))
# sd for same_sample
plot(hypothesis(brm_pi_task$posterior_model, "Intercept:disorderasd = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pi_task$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pi_task$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "same_sample"))
# sd for study_disorder
plot(hypothesis(brm_pi_task$posterior_model, "Intercept:disorderasd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pi_task$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pi_task$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "study_disorder"))
# sd for expt_unique
plot(hypothesis(brm_pi_task$posterior_model, "Intercept:dis_taskasd_freemonologicalproduction = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pi_task$posterior_model, "Intercept:dis_taskasd_socialinteraction = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pi_task$posterior_model, "Intercept:dis_taskrhd_constrainedproduction = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pi_task$posterior_model, "Intercept:dis_taskscz_constrainedproduction = 0", class = "sd", group = "expt_unique_dis"))
# nu
plot(hypothesis(brm_pi_task$posterior_model, "nu = 0", class = ""))

# language #
parnames(brm_pi_lang$posterior_model)
# summary
brm_pi_lang$posterior_summary
# mcmc_checks 
brm_pi_lang$mcmc_trace  
brm_pi_lang$mcmc_rank
# pretty mcmcm for paper in 1000x600
color_scheme_set("viridis")
mcmc_trace(brm_pi_lang$posterior_model, pars = vars(-contains("["), -contains("prior"), -contains("lp"), -contains("sigma"))) + theme_classic()
mcmc_rank_overlay(brm_pi_lang$posterior_model, pars = vars(-contains("["), -contains("prior"), -contains("lp"), -contains("sigma"))) + theme_classic()
# pp_checks 
brm_pi_lang$pp_checks
# b
plot(hypothesis(brm_pi_lang$posterior_model,"disorderasd:native_languageDanish = 0"))
plot(hypothesis(brm_pi_lang$posterior_model,"disorderasd:native_languageEnglish = 0"))
plot(hypothesis(brm_pi_lang$posterior_model,"disorderasd:native_languagePortuguese = 0"))
plot(hypothesis(brm_pi_lang$posterior_model,"disorderrhd:native_languageEnglish = 0"))
plot(hypothesis(brm_pi_lang$posterior_model,"disorderscz:native_languageEnglish = 0"))
# sd for same_sample
plot(hypothesis(brm_pi_lang$posterior_model, "Intercept:dis_langasd_Danish = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pi_lang$posterior_model, "Intercept:dis_langasd_English = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pi_lang$posterior_model, "Intercept:dis_langasd_Portuguese = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pi_lang$posterior_model, "Intercept:dis_langrhd_English = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pi_lang$posterior_model, "Intercept:dis_langscz_English = 0", class = "sd", group = "same_sample"))
# sd for study_disorder
plot(hypothesis(brm_pi_lang$posterior_model, "Intercept:disorderasd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pi_lang$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pi_lang$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "study_disorder"))
# sd for expt_unique
plot(hypothesis(brm_pi_lang$posterior_model, "Intercept:dis_langasd_Danish = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pi_lang$posterior_model, "Intercept:dis_langasd_English = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pi_lang$posterior_model, "Intercept:dis_langasd_Portuguese = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pi_lang$posterior_model, "Intercept:dis_langrhd_English = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pi_lang$posterior_model, "Intercept:dis_langscz_English = 0", class = "sd", group = "expt_unique_dis"))
# nu
plot(hypothesis(brm_pi_lang$posterior_model, "nu = 0", class = ""))

```

Quality checks: pitch variability
```{r}

# get unique values
unique(brm_pv_disorder$data$disorder) # asd, lhd, rhd, scz

# disorder #
# summary
brm_pv_disorder$posterior_summary
# mcmc_checks 
brm_pv_disorder$mcmc_trace  
brm_pv_disorder$mcmc_rank
# pretty mcmcm for paper in 1000x600
color_scheme_set("viridis")
mcmc_trace(brm_pv_disorder$posterior_model, pars = vars(-contains("["), -contains("prior"), -contains("lp"), -contains("sigma"))) + theme_classic()
mcmc_rank_overlay(brm_pv_disorder$posterior_model, pars = vars(-contains("["), -contains("prior"), -contains("lp"), -contains("sigma"))) + theme_classic()
# pp_checks 
brm_pv_disorder$pp_checks
# b: absolute values (effect sizes)
plot(hypothesis(brm_pv_disorder$posterior_model,"disorderasd = 0"))
plot(hypothesis(brm_pv_disorder$posterior_model,"disorderlhd = 0"))
plot(hypothesis(brm_pv_disorder$posterior_model,"disorderrhd = 0"))
plot(hypothesis(brm_pv_disorder$posterior_model,"disorderscz = 0"))
# sd for same sample
plot(hypothesis(brm_pv_disorder$posterior_model, "Intercept:disorderasd = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pv_disorder$posterior_model, "Intercept:disorderlhd = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pv_disorder$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pv_disorder$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "same_sample"))
# sd for study_disorder
plot(hypothesis(brm_pv_disorder$posterior_model, "Intercept:disorderasd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pv_disorder$posterior_model, "Intercept:disorderlhd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pv_disorder$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pv_disorder$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "study_disorder"))
# nu
plot(hypothesis(brm_pv_disorder$posterior_model, "nu = 0", class = ""))

# task type #
parnames(brm_pv_task$posterior_model)
# summary
brm_pv_task$posterior_summary
# mcmc_checks 
brm_pv_task$mcmc_trace  
brm_pv_task$mcmc_rank
# pretty mcmcm for paper in 1000x600
color_scheme_set("viridis")
mcmc_trace(brm_pv_task$posterior_model, pars = vars(-contains("["), -contains("prior"), -contains("lp"), -contains("sigma"))) + theme_classic()
mcmc_rank_overlay(brm_pv_task$posterior_model, pars = vars(-contains("["), -contains("prior"), -contains("lp"), -contains("sigma"))) + theme_classic()
# pp_checks 
brm_pv_task$pp_checks
# betas
plot(hypothesis(brm_pv_task$posterior_model,"disorderasd:task_typeconstrainedproduction = 0"))
plot(hypothesis(brm_pv_task$posterior_model,"disorderlhd:task_typeconstrainedproduction = 0"))
plot(hypothesis(brm_pv_task$posterior_model,"disorderrhd:task_typeconstrainedproduction = 0"))
plot(hypothesis(brm_pv_task$posterior_model,"disorderscz:task_typeconstrainedproduction = 0"))
plot(hypothesis(brm_pv_task$posterior_model,"disorderasd:task_typefreemonologicalproduction = 0"))
plot(hypothesis(brm_pv_task$posterior_model,"disorderrhd:task_typefreemonologicalproduction = 0"))
plot(hypothesis(brm_pv_task$posterior_model,"disorderscz:task_typefreemonologicalproduction = 0"))
plot(hypothesis(brm_pv_task$posterior_model,"disorderasd:task_typesocialinteraction = 0"))
plot(hypothesis(brm_pv_task$posterior_model,"disorderscz:task_typesocialinteraction = 0"))
# sd for same_sample
plot(hypothesis(brm_pv_task$posterior_model, "Intercept:disorderasd = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pv_task$posterior_model, "Intercept:disorderlhd = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pv_task$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pv_task$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "same_sample"))
# sd for study_disorder
plot(hypothesis(brm_pv_task$posterior_model, "Intercept:disorderasd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pv_task$posterior_model, "Intercept:disorderlhd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pv_task$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pv_task$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "study_disorder"))
# sd for expt_unqiue_dis
plot(hypothesis(brm_pv_task$posterior_model, "Intercept:dis_taskasd_constrainedproduction = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pv_task$posterior_model, "Intercept:dis_taskasd_freemonologicalproduction = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pv_task$posterior_model, "Intercept:dis_taskasd_socialinteraction = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pv_task$posterior_model, "Intercept:dis_tasklhd_constrainedproduction = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pv_task$posterior_model, "Intercept:dis_taskrhd_constrainedproduction = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pv_task$posterior_model, "Intercept:dis_taskrhd_freemonologicalproduction = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pv_task$posterior_model, "Intercept:dis_taskscz_constrainedproduction = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pv_task$posterior_model, "Intercept:dis_taskscz_freemonologicalproduction = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pv_task$posterior_model, "Intercept:dis_taskscz_socialinteraction = 0", class = "sd", group = "expt_unique_dis"))
# nu
plot(hypothesis(brm_pv_task$posterior_model, "nu = 0", class = ""))

# language #
# summary
brm_pv_lang$posterior_summary
# mcmc_checks 
brm_pv_lang$mcmc_trace  
brm_pv_lang$mcmc_rank
# pretty mcmcm for paper in 1000x600
color_scheme_set("viridis")
mcmc_trace(brm_pv_lang$posterior_model, pars = vars(-contains("["), -contains("prior"), -contains("lp"), -contains("sigma"))) + theme_classic()
mcmc_rank_overlay(brm_pv_lang$posterior_model, pars = vars(-contains("["), -contains("prior"), -contains("lp"), -contains("sigma"))) + theme_classic()
# pp_checks 
brm_pv_lang$pp_checks
# betas
plot(hypothesis(brm_pv_lang$posterior_model,"disorderasd:native_languageEnglish = 0"))
plot(hypothesis(brm_pv_lang$posterior_model,"disorderlhd:native_languageEnglish = 0"))
plot(hypothesis(brm_pv_lang$posterior_model,"disorderrhd:native_languageEnglish = 0"))
plot(hypothesis(brm_pv_lang$posterior_model,"disorderscz:native_languageEnglish = 0"))
plot(hypothesis(brm_pv_lang$posterior_model,"disorderasd:native_languageDanish = 0"))
plot(hypothesis(brm_pv_lang$posterior_model,"disorderasd:native_languageJapanese = 0"))
plot(hypothesis(brm_pv_lang$posterior_model,"disorderasd:native_languagePortuguese = 0"))
plot(hypothesis(brm_pv_lang$posterior_model,"disorderlhd:native_languageKorean = 0"))
plot(hypothesis(brm_pv_lang$posterior_model,"disorderrhd:native_languageKorean = 0"))
plot(hypothesis(brm_pv_lang$posterior_model,"disorderrhd:native_languagePolish = 0"))
plot(hypothesis(brm_pv_lang$posterior_model,"disorderrhd:native_languageThai = 0"))
# sd for same_sample
plot(hypothesis(brm_pv_lang$posterior_model, "Intercept:dis_langasd_Danish = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pv_lang$posterior_model, "Intercept:dis_langasd_English = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pv_lang$posterior_model, "Intercept:dis_langasd_Japanese = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pv_lang$posterior_model, "Intercept:dis_langasd_Portuguese = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pv_lang$posterior_model, "Intercept:dis_langlhd_English = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pv_lang$posterior_model, "Intercept:dis_langlhd_Korean = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pv_lang$posterior_model, "Intercept:dis_langrhd_English = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pv_lang$posterior_model, "Intercept:dis_langrhd_Korean = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pv_lang$posterior_model, "Intercept:dis_langrhd_Polish = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pv_lang$posterior_model, "Intercept:dis_langrhd_Thai = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pv_lang$posterior_model, "Intercept:dis_langscz_English = 0", class = "sd", group = "same_sample"))
# sd for study_disorder
plot(hypothesis(brm_pv_lang$posterior_model, "Intercept:disorderasd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pv_lang$posterior_model, "Intercept:disorderlhd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pv_lang$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pv_lang$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "study_disorder"))
# sd for expt unique
plot(hypothesis(brm_pv_lang$posterior_model, "Intercept:dis_langasd_Danish = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pv_lang$posterior_model, "Intercept:dis_langasd_English = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pv_lang$posterior_model, "Intercept:dis_langasd_Japanese = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pv_lang$posterior_model, "Intercept:dis_langasd_Portuguese = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pv_lang$posterior_model, "Intercept:dis_langlhd_English = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pv_lang$posterior_model, "Intercept:dis_langlhd_Korean = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pv_lang$posterior_model, "Intercept:dis_langrhd_English = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pv_lang$posterior_model, "Intercept:dis_langrhd_Korean = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pv_lang$posterior_model, "Intercept:dis_langrhd_Polish = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pv_lang$posterior_model, "Intercept:dis_langrhd_Thai = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pv_lang$posterior_model, "Intercept:dis_langscz_English = 0", class = "sd", group = "expt_unique_dis"))
# nu
plot(hypothesis(brm_pv_lang$posterior_model, "nu = 0", class = ""))

```

Adding the loo criterion to all of the models above to see, where we have problematic observations, which cannot be refitted because of too little data (to be removed for the model comparison models)
```{r}

# pause duration
brm_pd_disorder$posterior_model <- add_criterion(brm_pd_disorder$posterior_model, criterion = "loo", reloo = T, seed = TRUE)
brm_pd_task$posterior_model <- add_criterion(brm_pd_task$posterior_model, criterion = "loo", reloo = T, seed = TRUE)
brm_pd_lang$posterior_model <- add_criterion(brm_pd_lang$posterior_model, criterion = "loo", reloo = T, seed = TRUE)

# pitch
brm_pi_disorder$posterior_model <- add_criterion(brm_pi_disorder$posterior_model, criterion = "loo", reloo = T, seed = TRUE)
brm_pi_task$posterior_model <- add_criterion(brm_pi_task$posterior_model, criterion = "loo", reloo = T, seed = TRUE)
brm_pi_lang$posterior_model <- add_criterion(brm_pi_lang$posterior_model, criterion = "loo", reloo = T, seed = TRUE)

# pitch variability
brm_pv_disorder$posterior_model <- add_criterion(brm_pv_disorder$posterior_model, criterion = "loo", reloo = T, seed = TRUE) # did not do it
brm_pv_task$posterior_model <- add_criterion(brm_pv_task$posterior_model, criterion = "loo", reloo = T, seed = TRUE)
brm_pv_lang$posterior_model <- add_criterion(brm_pv_lang$posterior_model, criterion = "loo", reloo = T, seed = TRUE)

```

Removing problematic observations for data for model comparison
```{r}

# Pause Duration: No problem (reduced data is not needed)

# Pitch: Removing observations with n = 1 in dis_task or dis_lang
n_pi_lang_df <- df %>% subset(feature == "pitch") %>% group_by(disorder, native_language) %>% summarize(n_lang = n(), .groups = "drop_last")
n_pi_task_df <- df %>% subset(feature == "pitch") %>% group_by(disorder, task_type) %>% summarize(n_task = n(), .groups = "drop_last")

mc_pi_df <- df %>% subset(feature == "pitch") %>%
  merge(., n_pi_lang_df, by = c("disorder", "native_language")) %>%
  merge(., n_pi_task_df, by = c("disorder", "task_type")) %>%
  subset(n_lang != 1) %>% 
  subset(n_task != 1)

# Pitch Variability: Removing observations with n = 1 in dis_task or dis_lang
n_pv_lang_df <- df %>% subset(feature == "pitch_variability") %>% group_by(disorder, native_language) %>% summarize(n_lang = n(), .groups = "drop_last")
n_pv_task_df <- df %>% subset(feature == "pitch_variability") %>% group_by(disorder, task_type) %>% summarize(n_task = n(), .groups = "drop_last")

mc_pv_df <- df %>% subset(feature == "pitch_variability") %>%
  merge(., n_pv_lang_df, by = c("disorder", "native_language")) %>%
  merge(., n_pv_task_df, by = c("disorder", "task_type")) %>%
  subset(n_lang != 1) %>% 
  subset(n_task != 1)

```


Running the models for the model comparison (with the taken out data)
```{r}

# pause duration: do not need to run it again (brm models above work)
# mc_pd_disorder <- complete_brms(data = mc_df, feature = "pause_duration", formula = f_disorder, priors = model_priors, loo_criterion = T)
# mc_pd_task <- complete_brms(data = mc_df, feature = "pause_duration", formula = f_task, priors = model_priors, loo_criterion = T) 
# mc_pd_lang <- complete_brms(data = mc_df, feature = "pause_duration", formula = f_lang, priors = model_priors, loo_criterion = T)

# pitch
mc_pi_disorder <- complete_brms(data = mc_pi_df, feature = "pitch", formula = f_disorder, priors = model_priors, loo_criterion = T) 
mc_pi_task <- complete_brms(data = mc_pi_df, feature = "pitch", formula = f_task, priors = model_priors, loo_criterion = T) 
mc_pi_lang <- complete_brms(data = mc_pi_df, feature = "pitch", formula = f_lang, priors = model_priors, loo_criterion = T) 

saveRDS(mc_pi_disorder, "envr/mc_pi_disorder_2020_22_11.rds")
saveRDS(mc_pi_task, "envr/mc_pi_task_2020_22_11.rds")
saveRDS(mc_pi_lang, "envr/mc_pi_lang_2020_22_11.rds")

# pitch variability
mc_pv_disorder <- complete_brms(data = mc_pv_df, feature = "pitch_variability", formula = f_disorder, priors = model_priors, loo_criterion = T) 
mc_pv_task <- complete_brms(data = mc_pv_df, feature = "pitch_variability", formula = f_task, priors = model_priors, loo_criterion = T) 
mc_pv_lang <- complete_brms(data = mc_pv_df, feature = "pitch_variability", formula = f_lang, priors = model_priors, loo_criterion = T)

saveRDS(mc_pv_disorder, "envr/mc_pv_disorder_2020_22_11.rds")
saveRDS(mc_pv_task, "envr/mc_pv_task_2020_22_11.rds")
saveRDS(mc_pv_lang, "envr/mc_pv_lang_2020_22_11.rds")

```

Model Comparison
```{r}

# pause duration #
# task
loo_compare(brm_pd_disorder$posterior_model, brm_pd_task$posterior_model)
loo_model_weights(brm_pd_disorder$posterior_model, brm_pd_task$posterior_model)
# language
loo_compare(brm_pd_disorder$posterior_model, brm_pd_lang$posterior_model)
loo_model_weights(brm_pd_disorder$posterior_model, brm_pd_lang$posterior_model)
# all
loo_compare(brm_pd_disorder$posterior_model, brm_pd_task$posterior_model, brm_pd_lang$posterior_model)
loo_model_weights(brm_pd_disorder$posterior_model, brm_pd_task$posterior_model, brm_pd_lang$posterior_model)

# pitch #
# task
loo_compare(mc_pi_disorder$posterior_model, mc_pi_task$posterior_model)
loo_model_weights(mc_pi_disorder$posterior_model, mc_pi_task$posterior_model)
# language
loo_compare(mc_pi_disorder$posterior_model, mc_pi_lang$posterior_model)
loo_model_weights(mc_pi_disorder$posterior_model, mc_pi_lang$posterior_model)
# all
loo_compare(mc_pi_disorder$posterior_model, mc_pi_task$posterior_model, mc_pi_lang$posterior_model)
loo_model_weights(mc_pi_disorder$posterior_model, mc_pi_task$posterior_model, mc_pi_lang$posterior_model)

# pitch variability #
# task
loo_compare(mc_pv_disorder$posterior_model, mc_pv_task$posterior_model)
loo_model_weights(mc_pv_disorder$posterior_model, mc_pv_task$posterior_model)
# language
loo_compare(mc_pv_disorder$posterior_model, mc_pv_lang$posterior_model)
loo_model_weights(mc_pv_disorder$posterior_model, mc_pv_lang$posterior_model)
# all
loo_compare(mc_pv_disorder$posterior_model, mc_pv_task$posterior_model, mc_pv_lang$posterior_model)
loo_model_weights(mc_pv_disorder$posterior_model, mc_pv_task$posterior_model, mc_pv_lang$posterior_model)

```

Hypothesis testing: pause duration
```{r}

# n studies, papers, participants
# unique studies: 21
nrow(brm_pd_disorder$data) 
# papers: 12
length(unique(brm_pd_disorder$data$short_cite)) 
# participants 
pd_participants <- brm_pd_disorder$data %>% group_by(same_sample, disorder) %>%
  summarise(patients = head(n_1, 1),
            controls = head(n_2, 1))
#either counting the lhd damage controls (or not)
pd_participants$controls[pd_participants$disorder == "lhd"] <- NA
#total
sum(pd_participants$patients, na.rm = T) 
sum(pd_participants$controls, na.rm = T)  
# by disorder
pd_participants %>%
  group_by(disorder) %>%
  summarise(patients = sum(patients),
            controls = sum(controls, na.rm = T),
            total = sum(patients) + sum(controls, na.rm = T), .groups = "drop_last")

# summary 
brm_pd_disorder$posterior_summary

## hypothesis testing: alpha = 0.025 for 95% CIs ##

# overall ES in disorder model #
hypothesis(brm_pd_disorder$posterior_model, "disorderrhd < 0", alpha = 0.025)
hypothesis(brm_pd_disorder$posterior_model, "disorderlhd > 0", alpha = 0.025)
hypothesis(brm_pd_disorder$posterior_model, "disorderscz > 0", alpha = 0.025)

# comparison of ES in disorder model #
conditional_effects(brm_pd_disorder$posterior_model, "disorder")
hypothesis(brm_pd_disorder$posterior_model, "disorderscz > disorderlhd", alpha = 0.025) 
hypothesis(brm_pd_disorder$posterior_model, "disorderscz > disorderrhd", alpha = 0.025) 
hypothesis(brm_pd_disorder$posterior_model, "disorderlhd > disorderrhd", alpha = 0.025)

# overall ES in task model #
hypothesis(brm_pd_task$posterior_model, "disorderrhd:task_typeconstrainedproduction < 0", alpha = 0.025)
hypothesis(brm_pd_task$posterior_model, "disorderlhd:task_typeconstrainedproduction > 0", alpha = 0.025)

# comparison of ES in task type model #
brm_pd_task$posterior_summary$fixed
brm_pd_task_2$posterior_summary$fixed
brm_pd_disorder$data %>% group_by(disorder, task_type) %>% summarise(n = n())
parnames(brm_pd_task$posterior_model)
conditional_effects(brm_pd_task$posterior_model, "disorder:task_type")
hypothesis(brm_pd_task$posterior_model, "disorderlhd:task_typeconstrainedproduction > disorderrhd:task_typeconstrainedproduction", alpha = 0.025) 

# overall ES in task model #
hypothesis(brm_pd_lang$posterior_model, "disorderrhd:native_languageEnglish < 0", alpha = 0.025)
hypothesis(brm_pd_lang$posterior_model, "disorderscz:native_languageEnglish > 0", alpha = 0.025)

# comparison of ES in language model #
brm_pd_lang$posterior_summary
brm_pd_disorder$data %>% group_by(disorder, native_language) %>% summarise(n = n())
parnames(brm_pd_lang$posterior_model)
conditional_effects(brm_pd_lang$posterior_model, "disorder:native_language")
hypothesis(brm_pd_lang$posterior_model, "disorderscz:native_languageEnglish > disorderrhd:native_languageEnglish", alpha = 0.025)


```

Hypothesis testing: pitch
```{r}

# n studies, papers, participants
# unique studies: 40
nrow(brm_pi_disorder$data) 
# papers: 23
length(unique(brm_pi_disorder$data$short_cite)) 
# participants 
pi_participants <- brm_pi_disorder$data %>% group_by(same_sample, disorder) %>%
  summarise(patients = head(n_1, 1),
            controls = head(n_2, 1))
# no lhd in this data
#total
sum(pi_participants$patients, na.rm = T) #591
sum(pi_participants$controls, na.rm = T) #528
# by disorder
pi_participants %>%
  group_by(disorder) %>%
  summarise(patients = sum(patients),
            controls = sum(controls, na.rm = T),
            total = sum(patients) + sum(controls, na.rm = T), .groups = "drop_last")

# summary
brm_pi_disorder$posterior_summary

## hypothesis testing: alpha = 0.025 for 95% CIs ##

# overall ES in the disorder model #
hypothesis(brm_pi_disorder$posterior_model, "disorderrhd > 0", alpha = 0.025)
hypothesis(brm_pi_disorder$posterior_model, "disorderasd > 0", alpha = 0.025)
hypothesis(brm_pi_disorder$posterior_model, "disorderscz > 0", alpha = 0.025)

# comparison of ES in disorder model #
conditional_effects(brm_pi_disorder$posterior_model, "disorder")
hypothesis(brm_pi_disorder$posterior_model, "disorderrhd > disorderasd", alpha = 0.025)
hypothesis(brm_pi_disorder$posterior_model, "disorderrhd > disorderscz", alpha = 0.025)
hypothesis(brm_pi_disorder$posterior_model, "disorderasd > disorderscz", alpha = 0.025)

# task type model #
brm_pi_disorder$data %>% group_by(disorder, task_type) %>% summarise(n = n())
parnames(brm_pi_task$posterior_model)
conditional_effects(brm_pi_task$posterior_model, "disorder:task_type")
# NO TESTING POSSIBLE

# overall ES in the language model #
hypothesis(brm_pi_lang$posterior_model, "disorderrhd:native_languageEnglish > 0", alpha = 0.025)
hypothesis(brm_pi_lang$posterior_model, "disorderasd:native_languageEnglish > 0", alpha = 0.025)

# comparison of ES in language model #
brm_pi_lang$posterior_summary
brm_pi_disorder$data %>% group_by(disorder, native_language) %>% summarise(n = n())
parnames(brm_pi_lang$posterior_model)
conditional_effects(brm_pi_lang$posterior_model, "disorder:native_language")
hypothesis(brm_pi_lang$posterior_model, "disorderrhd:native_languageEnglish > disorderasd:native_languageEnglish", alpha = 0.025)

```


PITCH VARIABILITY: HYPOTHESIS TESTING
```{r}

# n studies, papers, participants
# unique studies: 84
nrow(brm_pv_disorder$data) 
# papers: 41
length(unique(brm_pv_disorder$data$short_cite)) 
# participants 
pv_participants <- brm_pv_disorder$data %>% group_by(same_sample, disorder) %>%
  summarise(patients = head(n_1, 1),
            controls = head(n_2, 1))
# either counting the lhd damage controls (or not)
pv_participants$controls[pv_participants$disorder == "lhd"] <- NA
# total
sum(pv_participants$patients, na.rm = T) # 1214
sum(pv_participants$controls, na.rm = T) # 941
# by disorder
pv_participants %>%
  group_by(disorder) %>%
  summarise(patients = sum(patients),
            controls = sum(controls, na.rm = T),
            total = sum(patients) + sum(controls, na.rm = T), .groups = "drop_last")

# summary
brm_pv_disorder$posterior_summary

## hypothesis testing: alpha = 0.025 for 95% CIs ##

# overall ES of disorder model #
hypothesis(brm_pv_disorder$posterior_model, "disorderasd > 0", alpha = 0.025)
hypothesis(brm_pv_disorder$posterior_model, "disorderrhd < 0", alpha = 0.025)
hypothesis(brm_pv_disorder$posterior_model, "disorderlhd < 0", alpha = 0.025)
hypothesis(brm_pv_disorder$posterior_model, "disorderscz < 0", alpha = 0.025)

# comparison of ES in disorder model #
brm_pv_disorder$posterior_summary
conditional_effects(brm_pv_disorder$posterior_model, "disorder")
hypothesis(brm_pv_disorder$posterior_model, "disorderasd > disorderrhd", alpha = 0.025) 
hypothesis(brm_pv_disorder$posterior_model, "disorderasd > disorderlhd", alpha = 0.025) 
hypothesis(brm_pv_disorder$posterior_model, "disorderasd > disorderscz", alpha = 0.025) 
hypothesis(brm_pv_disorder$posterior_model, "disorderrhd > disorderlhd", alpha = 0.025) 
hypothesis(brm_pv_disorder$posterior_model, "disorderrhd > disorderscz", alpha = 0.025) 
hypothesis(brm_pv_disorder$posterior_model, "disorderlhd > disorderscz", alpha = 0.025)

# overall ES of task type model #
hypothesis(brm_pv_task$posterior_model, "disorderrhd:task_typeconstrainedproduction < 0", alpha = 0.025)
hypothesis(brm_pv_task$posterior_model, "disorderlhd:task_typeconstrainedproduction < 0", alpha = 0.025)
hypothesis(brm_pv_task$posterior_model, "disorderasd:task_typefreemonologicalproduction > 0", alpha = 0.025)
hypothesis(brm_pv_task$posterior_model, "disorderscz:task_typefreemonologicalproduction < 0", alpha = 0.025)

# comparison of ES in task type model #
brm_pv_task$posterior_summary
brm_pv_disorder$data %>% group_by(disorder, task_type) %>% summarise(n = n())
parnames(brm_pv_task$posterior_model)
conditional_effects(brm_pv_task$posterior_model, "disorder:task_type")
hypothesis(brm_pv_task$posterior_model, "disorderrhd:task_typeconstrainedproduction > disorderlhd:task_typeconstrainedproduction", alpha = 0.025)
hypothesis(brm_pv_task$posterior_model, "disorderasd:task_typefreemonologicalproduction > disorderscz:task_typefreemonologicalproduction", alpha = 0.025)

# overall ES of language model #
hypothesis(brm_pv_lang$posterior_model, "disorderasd:native_languageEnglish > 0", alpha = 0.025)
hypothesis(brm_pv_lang$posterior_model, "disorderrhd:native_languageEnglish < 0", alpha = 0.025)
hypothesis(brm_pv_lang$posterior_model, "disorderlhd:native_languageEnglish < 0", alpha = 0.025)
hypothesis(brm_pv_lang$posterior_model, "disorderscz:native_languageEnglish < 0", alpha = 0.025)

# comparison of ES in language model #
brm_pv_lang$posterior_summary
brm_pv_disorder$data %>% group_by(disorder, native_language) %>% summarise(n = n())
parnames(brm_pv_lang$posterior_model)
conditional_effects(brm_pv_lang$posterior_model, "disorder:native_language")
hypothesis(brm_pv_lang$posterior_model, "disorderasd:native_languageEnglish > disorderrhd:native_languageEnglish", alpha = 0.025)
hypothesis(brm_pv_lang$posterior_model, "disorderasd:native_languageEnglish > disorderlhd:native_languageEnglish", alpha = 0.025)
hypothesis(brm_pv_lang$posterior_model, "disorderasd:native_languageEnglish > disorderscz:native_languageEnglish", alpha = 0.025) 
hypothesis(brm_pv_lang$posterior_model, "disorderrhd:native_languageEnglish > disorderlhd:native_languageEnglish", alpha = 0.025)
hypothesis(brm_pv_lang$posterior_model, "disorderrhd:native_languageEnglish > disorderscz:native_languageEnglish", alpha = 0.025)
hypothesis(brm_pv_lang$posterior_model, "disorderlhd:native_languageEnglish > disorderscz:native_languageEnglish", alpha = 0.025)

```
