---
title: "Model analysis"
output: html_document
editor_options: 
  chunk_output_type: console
---

### Packages + Functions
```{r setup, include=FALSE}
pacman::p_load(
  brms,
  #rethinking,
  tidyverse,
  bayesplot,
  #viridis,
  #dplyr,
  #data.table,
  ggplot2,
  BayesCombo,
  #beepr, #not in R version 4.0.2?
  patchwork,
  #modeest,
  renv,
  rlist,
  bayestestR
)
```

Calculate effect size RF's way
```{r}
# Calculate standardized effect sizes, variance and standard errors

ES_calc <- function(d, feature = "pitch"){ #function(d,Name="pitch variability")
  
  # Calculate standardized effect sizes
  d = escalc(
    'SMD',
    n1i = d$n_1, n2i = d$n_2,
    m1i = d$x_1, m2i = d$x_2,
    sd1i = d$SD_1, sd2i = d$SD_2,
    data = d
  )
  
  d$StandardError=summary(d)$sei
  d = d %>% dplyr::rename(EffectSize=yi,Variance=vi)
  
  return(d)
}

### Exploring Data
```

Reading data, adding important columns
```{r}
# Reading data
df <- read.csv("data/data_calc_16_11_2020.csv")

# Adding study_disorder
df$study_disorder <- paste(df$study_ID, df$disorder, sep = "_")

# Adding expt_unique_dis
df$expt_unique_dis <- paste(df$expt_unique, df$disorder, sep = "_")

# Adding mo_task_type (ordered factor with three levels)
df$mo_task_type <- factor(df$task_type, order = T,
                            levels = c("constrained production",
                                       "free monological production",
                                       "social interaction"))

df$native_language <- as.factor(df$native_language)
str(df$native_language)

df$dis_task <- paste(df$disorder, df$task_type)
df$dis_lang <- paste(df$disorder, df$native_language)

# Summary statistics (could be used on website as priors if brms, but here we want it by the subsetted feature)
# mean(data$EffectSize)
# sd(data$EffectSize)
```

Possible features
```{r}
# Features with 3 or more disorders/MAs with 5 or more studies/rows (to be analysed) and their effect sizes
features <- data %>% 
  group_by(disorder, feature) %>% 
  summarise(
    n_studies = n(),
    .groups = "drop_last"
  ) %>% 
  filter(n_studies >= 5)

possible_features <- features %>% 
  group_by(feature) %>% 
  summarise(
    n_disorders = n(),
    disorders = list(disorder),
    .groups = "drop_last"
  ) %>% 
  filter(n_disorders >= 3)

# Which are these possible features?
possible_features$feature
# pause_duration, pitch, pitch_variability 

# Adding effect sizes (from website calculation)
# possible_features$es_c_asd <- c(0.00, NA, NA, 0.21, 0.38, 0.46, 0.86, NA, -0.10)
# possible_features$es_g_asd <- c(-0.01, NA, NA, 0.21, 0.37, 0.45, 0.84, NA, -0.10)
# possible_features$es_c_lhd <- c(NA, 0.68, 0.52, NA, NA, -0.41, NA, -1.44, NA)
# possible_features$es_g_lhd <- c(NA, 0.64, 0.50, NA, NA, -0.40, NA, -1.36, NA)
# possible_features$es_c_rhd <- c(-0.37, -3.00, -0.60, NA, 0.68, -0.34, 0.10, -1.67, NA)
# possible_features$es_g_rhd <- c(-0.35, -2.84, -0.57, NA, 0.64, -0.33, 0.09, -1.58, NA)
# possible_features$es_c_scz <- c(NA, 1.10, 1.78, 0.17, 0.16, -0.58, -0.15, NA, -0.87)
# possible_features$es_g_scz <- c(NA, 1.08, 1.72, 0.17, 0.15, -0.57, -0.15, NA, -0.86)
```

```{r}
# Subsetting (examples)
# pause_duration <- subset(data, feature == "pause_duration")
# pitch <- subset(data, feature == "pitch")
# pitch_var <- subset(data, feature == "pitch_variability")
```

Functions
```{r}
# subset for voice feature
feature_subset <- function(dataset, feature_name) {
  invisible(
    subset(dataset, feature == feature_name) %>%
    group_by(disorder) %>%
    filter(n() >= 5))
}

# run models (can be used for prior and real model)
brm_fit <- function(def_formula, data_subset, def_priors, sample_prior) {
  if (sample_prior == "only"){
    model <- brm(
      formula = def_formula,
      data = data_subset,
      family = student(),
      prior = def_priors,
      sample_prior = "only",
      seed = 28,
      chains = 4,
      cores = 6,
      iter = 4000,
      control = list(
        max_treedepth = 20,
        adapt_delta=0.98))
  }
  if (sample_prior == T) {
    model <- brm(
      formula = def_formula,
      data = data_subset,
      family = student(),
      prior = def_priors,
      sample_prior = T,
      seed = 28,
      chains = 4,
      cores = 6,
      iter = 4000,
      control = list(
        max_treedepth = 20,
        adapt_delta=0.98))
  }
  return(model)
}

# complete function
complete_brms <- function(data, feature, formula, priors, loo_criterion) {
  
  subset <- feature_subset(dataset = data, feature_name = feature) 
  
  if ("native_language" %in% formula){
    # make languages with 1 into "Other"
    n_lang_df <- subset %>% group_by(native_language) %>% summarize(n_lang = n(), .groups = "drop_last")
    subset <- merge(subset, n_lang_df, by = "native_language")
    subset$native_language[subset$n_lang == 1] <- "Other"
  }
  
  prior_model <- brm_fit(def_formula = formula, data_subset = subset, def_priors = priors, sample_prior = "only")
  
  posterior_model <- brm_fit(def_formula = formula, data_subset = subset, def_priors = priors, sample_prior = T)
  
  pp_checks <- pp_check(prior_model, nsamples = 1000) + pp_check(posterior_model, nsamples = 1000)
  
  summary <- summary(posterior_model)
  
  mcmc_trace <- mcmc_trace(posterior_model) + theme_classic()
  
  mcmc_rank <- mcmc_rank_overlay(posterior_model) + theme_classic()
  
  if(loo_criterion == T){
    posterior_model <- add_criterion(posterior_model, criterion = "loo", reloo = TRUE, seed = TRUE)
  }
  
  return_objects <- list("data" = subset,
                         "feature" = feature,
                         "prior_model" = prior_model,
                         "posterior_model" = posterior_model,
                         "pp_checks" = pp_checks, 
                         "posterior_summary" = summary,
                         "mcmc_trace" = mcmc_trace, 
                         "mcmc_rank" = mcmc_rank
                         )
  return(return_objects)
}
```

Defining inputs to function
```{r}
# Formulas
f_disorder <- bf(g_calc|se(g_var_calc) ~ 0 + disorder + (1|gr(same_sample, by = disorder)) + (1|gr(study_disorder, by = disorder)) + (1|gr(expt_unique_dis, by = disorder)))

f_task <- bf(g_calc|se(g_var_calc) ~ 0 + disorder : task_type + (1|gr(same_sample, by = disorder)) + (1|gr(study_disorder, by = disorder)) + (1|gr(expt_unique_dis, by = dis_task)))
#f_task <- bf(g_calc|se(g_var_calc) ~ 0 + disorder : task_type + (1|gr(same_sample, by = disorder)) + (1|gr(study_disorder, by = disorder)) + (1|gr(expt_unique_dis, by = disorder)))

f_language <- bf(g_calc|se(g_var_calc) ~ 0 + disorder : native_language + (1|gr(same_sample, by = dis_lang)) + (1|gr(study_disorder, by = disorder)) + (1|gr(expt_unique_dis, by = dis_lang)))
#f_language2 <- bf(g_calc|se(g_var_calc) ~ 0 + disorder : native_language + (1|gr(same_sample, by = disorder)) + (1|gr(study_disorder, by = disorder)) + (1|gr(expt_unique_dis, by = disorder)))


# Priors
model_priors <- c(
  prior(normal(0, 2.5), class = b)
  #using default sd because we expect outliers
  )
```

Restoring the saved objects
```{r}
# Restore the saved object under a different name
brm_pd_disorder <- readRDS("envr/brm_pd_disorder_2020_16_11.rds")
brm_pd_task <- readRDS("envr/brm_pd_task_2020_15_11.rds")
brm_pd_task_no_by <- readRDS("envr/brm_pd_task_no_by_2020_15_11.rds")
```

Running the three models, divided by feature
```{r}
# Pause duration
brm_pd_disorder <- complete_brms(data = df, feature = "pause_duration", formula = f_disorder, priors = model_priors, loo_criterion = T) #fine QC
saveRDS(brm_pd_disorder, "envr/brm_pd_disorder_2020_17_11.rds")

brm_pd_task <- complete_brms(data = df, feature = "pause_duration", formula = f_task, priors = model_priors, loo_criterion = F) #fine QC
saveRDS(brm_pd_task, "envr/brm_pd_task_2020_17_11.rds")
brm_pd_task_no_by <- complete_brms(data = df, feature = "pause_duration", formula = f_task_no_by, priors = model_priors, loo_criterion = F) #fine QC
saveRDS(brm_pd_task_no_by, "envr/brm_pd_task_no_by_2020_17_11.rds")

brm_pd_language <- complete_brms(data = df, feature = "pause_duration", formula = f_language, priors = model_priors, loo_criterion = F) #fine QC (a bit tight)
saveRDS(brm_pd_language, "envr/brm_pd_language_2020_17_11.rds")
brm_pd_language2 <- complete_brms(data = df, feature = "pause_duration", formula = f_language2, priors = model_priors, loo_criterion = F) #fine QC (a bit more tight)
saveRDS(brm_pd_language2, "envr/brm_pd_language2_2020_17_11.rds")
brm_pd_language_no_by <- complete_brms(data = df, feature = "pause_duration", formula = f_language_no_by, priors = model_priors, loo_criterion = F) #fine QC (a bit tight)
saveRDS(brm_pd_language_no_by, "envr/brm_pd_language_no_by_2020_17_11.rds")

# brm_pd_disorder$posterior_model <- add_criterion(brm_pd_disorder$posterior_model, criterion = "loo")
# brm_pd_task$posterior_model <- add_criterion(brm_pd_task$posterior_model, criterion = "loo")
# brm_pd_task_no_by$posterior_model <- add_criterion(brm_pd_task_no_by$posterior_model, criterion = "loo")
# brm_pd_language$posterior_model <- add_criterion(brm_pd_language$posterior_model, criterion = "loo")
# brm_pd_language2$posterior_model <- add_criterion(brm_pd_language2$posterior_model, criterion = "loo")
# brm_pd_language_no_by$posterior_model <- add_criterion(brm_pd_language_no_by$posterior_model, criterion = "loo)


# Pitch
brm_p_disorder <- complete_brms(data = df, feature = "pitch", formula = f_disorder, priors = model_priors, loo_criterion = F) #fine QC
saveRDS(brm_p_disorder, "envr/brm_p_disorder_2020_17_11.rds")

brm_p_task <- complete_brms(data = df, feature = "pitch", formula = f_task, priors = model_priors, loo_criterion = F) #fine QC
saveRDS(brm_p_task, "envr/brm_p_task_2020_17_11.rds")
brm_p_task_no_by <- complete_brms(data = df, feature = "pitch", formula = f_task_no_by, priors = model_priors, loo_criterion = F) #fine QC
saveRDS(brm_p_task_no_by, "envr/brm_p_task_no_by_2020_17_11.rds")

brm_p_language <- complete_brms(data = df, feature = "pitch", formula = f_language, priors = model_priors, loo_criterion = F) #fine QC
saveRDS(brm_p_language, "envr/brm_p_language_2020_17_11.rds")
brm_p_language2 <- complete_brms(data = df, feature = "pitch", formula = f_language2, priors = model_priors, loo_criterion = F) #fine QC
saveRDS(brm_p_language2, "envr/brm_p_language2_2020_17_11.rds")
brm_p_language_no_by <- complete_brms(data = df, feature = "pitch", formula = f_language_no_by, priors = model_priors, loo_criterion = F) #fine QC
saveRDS(brm_p_language_no_by, "envr/brm_p_language_no_by_2020_17_11.rds")



# Pitch variability
brm_pv_disorder <- complete_brms(data = df, feature = "pitch_variability", formula = f_disorder, priors = model_priors, loo_criterion = F) #fine QC
saveRDS(brm_pv_disorder, "envr/brm_pv_disorder_2020_17_11.rds")

brm_pv_task <- complete_brms(data = df, feature = "pitch_variability", formula = f_task, priors = model_priors, loo_criterion = F) #fine QC
saveRDS(brm_pv_task, "envr/brm_pv_task_2020_17_11.rds")
brm_pv_task_no_by <- complete_brms(data = df, feature = "pitch_variability", formula = f_task_no_by, priors = model_priors, loo_criterion = F) #fine QC
saveRDS(brm_pv_task_no_by, "envr/brm_pv_task_no_by_2020_17_11.rds")

brm_pv_language <- complete_brms(data = df, feature = "pitch_variability", formula = f_language, priors = model_priors, loo_criterion = F) #fine QC
saveRDS(brm_pv_language, "envr/brm_pv_language_2020_17_11.rds")
brm_pv_language2 <- complete_brms(data = df, feature = "pitch_variability", formula = f_language2, priors = model_priors, loo_criterion = F) #fine QC
saveRDS(brm_pv_language2, "envr/brm_pv_language2_2020_17_11.rds")
brm_pv_language_no_by <- complete_brms(data = df, feature = "pitch_variability", formula = f_language_no_by, priors = model_priors, loo_criterion = F) #fine QC
saveRDS(brm_pv_language_no_by, "envr/brm_pv_language_no_by_2020_17_11.rds")

#  Fejl: New factor levels are not allowed.
# Levels allowed: 'Cantonese', 'Danish', 'Dutch', 'English', 'French', 'Hebrew', 'Japanese', 'Korean', 'Polish', 'Portuguese', 'Swedish', 'Thai'
# Levels found: 'Cantonese', 'Danish', 'Dutch', 'English', 'French', 'Hebrew', 'Japanese', 'Korean', 'Polish', 'Portuguese', '##Spanish##', 'Swedish', 'Thai'
```

#Quality checking
Pause duration
```{r}
# brm_pd_disorder (~ 0 + disorder)
brm_pd_disorder$posterior_summary # Rhat = 1.00, ESS > 2400
brm_pd_disorder$pp_checks

brm_pd_disorder$mcmc_trace
brm_pd_disorder$mcmc_rank

parnames(brm_pd_disorder$posterior_model)

plot(hypothesis(brm_pd_disorder$posterior_model,"disorderlhd = 0"))
plot(hypothesis(brm_pd_disorder$posterior_model,"disorderrhd = 0"))
plot(hypothesis(brm_pd_disorder$posterior_model,"disorderscz = 0"))

plot(hypothesis(brm_pd_disorder$posterior_model, "Intercept:disorderlhd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pd_disorder$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pd_disorder$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "study_disorder"))

plot(hypothesis(brm_pd_disorder$posterior_model, "Intercept:disorderlhd = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pd_disorder$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pd_disorder$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "same_sample"))

plot(hypothesis(brm_pd_disorder$posterior_model, "Intercept:disorderlhd = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pd_disorder$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pd_disorder$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "expt_unique_dis"))

plot(hypothesis(brm_pd_disorder$posterior_model, "nu = 0", class = ""))


# brm_pd_task (~ 0 + disorder : task_type)
brm_pd_task$posterior_summary #Rhat = 1.00, ESS > 2500
brm_pd_task$pp_checks

brm_pd_task$mcmc_trace
brm_pd_task$mcmc_rank

parnames(brm_pd_task$posterior_model)

plot(hypothesis(brm_pd_task$posterior_model,"disorderlhd:task_typeconstrainedproduction = 0"))
plot(hypothesis(brm_pd_task$posterior_model,"disorderrhd:task_typeconstrainedproduction = 0"))
plot(hypothesis(brm_pd_task$posterior_model,"disorderscz:task_typeconstrainedproduction = 0"))
plot(hypothesis(brm_pd_task$posterior_model,"disorderscz:task_typefreemonologicalproduction = 0"))
plot(hypothesis(brm_pd_task$posterior_model,"disorderscz:task_typesocialinteraction = 0"))

plot(hypothesis(brm_pd_task$posterior_model, "Intercept:disorderlhd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pd_task$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pd_task$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "study_disorder"))

plot(hypothesis(brm_pd_task$posterior_model, "Intercept:disorderlhd = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pd_task$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pd_task$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "same_sample"))

plot(hypothesis(brm_pd_task$posterior_model, "Intercept:disorderlhd = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pd_task$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pd_task$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "expt_unique_dis"))

plot(hypothesis(brm_pd_task$posterior_model, "nu = 0", class = ""))



# brm_pd_language (~ 0 + disorder : native_language)
brm_pd_language$posterior_summary #Rhat = 1.00, ESS > 3100
brm_pd_language$pp_checks

brm_pd_language$mcmc_trace
brm_pd_language$mcmc_rank

parnames(brm_pd_language$posterior_model)

plot(hypothesis(brm_pd_language$posterior_model,"disorderlhd:native_languageEnglish = 0"))
plot(hypothesis(brm_pd_language$posterior_model,"disorderlhd:native_languageKorean = 0"))
plot(hypothesis(brm_pd_language$posterior_model,"disorderrhd:native_languageEnglish = 0"))
plot(hypothesis(brm_pd_language$posterior_model,"disorderrhd:native_languageKorean = 0"))
plot(hypothesis(brm_pd_language$posterior_model,"disorderscz:native_languageEnglish = 0"))
plot(hypothesis(brm_pd_language$posterior_model,"disorderscz:native_languageGerman = 0")) # a bit tight

plot(hypothesis(brm_pd_language$posterior_model, "Intercept:disorderlhd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pd_language$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pd_language$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "study_disorder"))

plot(hypothesis(brm_pd_language$posterior_model, "Intercept:disorderlhd = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pd_language$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pd_language$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "same_sample"))

plot(hypothesis(brm_pd_language$posterior_model, "Intercept:disorderlhd = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pd_language$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pd_language$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "expt_unique_dis"))

plot(hypothesis(brm_pd_language$posterior_model, "nu = 0", class = ""))
```
Pause Duration (extra models)
```{r}
# brm_pd_task_no_by_no_by (~ 0 + disorder : task_type)
brm_pd_task_no_by$posterior_summary #Rhat = 1.00, ESS > 1700
brm_pd_task_no_by$pp_checks

brm_pd_task_no_by$mcmc_trace
brm_pd_task_no_by$mcmc_rank

parnames(brm_pd_task_no_by$posterior_model)

plot(hypothesis(brm_pd_task_no_by$posterior_model,"disorderlhd:task_typeconstrainedproduction = 0"))
plot(hypothesis(brm_pd_task_no_by$posterior_model,"disorderrhd:task_typeconstrainedproduction = 0"))
plot(hypothesis(brm_pd_task_no_by$posterior_model,"disorderscz:task_typeconstrainedproduction = 0"))
plot(hypothesis(brm_pd_task_no_by$posterior_model,"disorderscz:task_typefreemonologicalproduction = 0"))
plot(hypothesis(brm_pd_task_no_by$posterior_model,"disorderscz:task_typesocialinteraction = 0"))

plot(hypothesis(brm_pd_task_no_by$posterior_model, "Intercept = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pd_task_no_by$posterior_model, "Intercept = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pd_task_no_by$posterior_model, "Intercept = 0", class = "sd", group = "expt_unique_dis"))

plot(hypothesis(brm_pd_task_no_by$posterior_model, "nu = 0", class = ""))

# brm_pd_language2 ()
brm_pd_language2$posterior_summary #Rhat = 1.00, ESS > 2900
brm_pd_language2$pp_checks

brm_pd_language2$mcmc_trace
brm_pd_language2$mcmc_rank

parnames(brm_pd_language2$posterior_model)

plot(hypothesis(brm_pd_language2$posterior_model,"disorderlhd:native_languageEnglish = 0"))
plot(hypothesis(brm_pd_language2$posterior_model,"disorderlhd:native_languageKorean = 0"))
plot(hypothesis(brm_pd_language2$posterior_model,"disorderrhd:native_languageEnglish = 0"))
plot(hypothesis(brm_pd_language2$posterior_model,"disorderrhd:native_languageKorean = 0"))
plot(hypothesis(brm_pd_language2$posterior_model,"disorderscz:native_languageEnglish = 0"))
plot(hypothesis(brm_pd_language2$posterior_model,"disorderscz:native_languageGerman = 0")) # TIGHT

plot(hypothesis(brm_pd_language2$posterior_model, "Intercept:disorderlhd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pd_language2$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pd_language2$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "study_disorder"))

plot(hypothesis(brm_pd_language2$posterior_model, "Intercept:dis_langlhdEnglish = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pd_language2$posterior_model, "Intercept:dis_langlhdKorean = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pd_language2$posterior_model, "Intercept:dis_langrhdEnglish = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pd_language2$posterior_model, "Intercept:dis_langrhdKorean = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pd_language2$posterior_model, "Intercept:dis_langsczEnglish = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pd_language2$posterior_model, "Intercept:dis_langsczGerman = 0", class = "sd", group = "same_sample"))

plot(hypothesis(brm_pd_language2$posterior_model, "Intercept:dis_langlhdEnglish = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pd_language2$posterior_model, "Intercept:dis_langlhdKorean = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pd_language2$posterior_model, "Intercept:dis_langrhdEnglish = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pd_language2$posterior_model, "Intercept:dis_langrhdKorean = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pd_language2$posterior_model, "Intercept:dis_langsczEnglish = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pd_language2$posterior_model, "Intercept:dis_langsczGerman = 0", class = "sd", group = "expt_unique_dis"))

plot(hypothesis(brm_pd_language2$posterior_model, "nu = 0", class = ""))


# brm_pd_language_no_by ()
brm_pd_language_no_by$posterior_summary #Rhat = 1.00, ESS > 1700
brm_pd_language_no_by$pp_checks

brm_pd_language_no_by$mcmc_trace
brm_pd_language_no_by$mcmc_rank

parnames(brm_pd_language_no_by$posterior_model)

plot(hypothesis(brm_pd_language_no_by$posterior_model,"disorderlhd:native_languageEnglish = 0"))
plot(hypothesis(brm_pd_language_no_by$posterior_model,"disorderlhd:native_languageKorean = 0"))
plot(hypothesis(brm_pd_language_no_by$posterior_model,"disorderrhd:native_languageEnglish = 0"))
plot(hypothesis(brm_pd_language_no_by$posterior_model,"disorderrhd:native_languageKorean = 0"))
plot(hypothesis(brm_pd_language_no_by$posterior_model,"disorderscz:native_languageEnglish = 0"))
plot(hypothesis(brm_pd_language_no_by$posterior_model,"disorderscz:native_languageGerman = 0")) # a bit tight

plot(hypothesis(brm_pd_language_no_by$posterior_model, "Intercept = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pd_language_no_by$posterior_model, "Intercept = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pd_language_no_by$posterior_model, "Intercept = 0", class = "sd", group = "expt_unique_dis"))

plot(hypothesis(brm_pd_language_no_by$posterior_model, "nu = 0", class = ""))
```


Pitch
```{r}
# brm_p_disorder (~ 0 + disorder)
brm_p_disorder$posterior_summary #Rhat = 1.00, ESS > 1300
brm_p_disorder$pp_checks

brm_p_disorder$mcmc_trace
brm_p_disorder$mcmc_rank

parnames(brm_p_disorder$posterior_model)

plot(hypothesis(brm_p_disorder$posterior_model,"disorderasd = 0"))
plot(hypothesis(brm_p_disorder$posterior_model,"disorderrhd = 0"))
plot(hypothesis(brm_p_disorder$posterior_model,"disorderscz = 0"))

plot(hypothesis(brm_p_disorder$posterior_model, "Intercept:disorderasd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_p_disorder$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_p_disorder$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "study_disorder"))

plot(hypothesis(brm_p_disorder$posterior_model, "Intercept:disorderasd = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_p_disorder$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_p_disorder$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "same_sample"))

plot(hypothesis(brm_p_disorder$posterior_model, "Intercept:disorderasd = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_p_disorder$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_p_disorder$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "expt_unique_dis"))

plot(hypothesis(brm_p_disorder$posterior_model, "nu = 0", class = ""))


# brm_p_task (~ 0 + disorder : task_type)
brm_p_task$posterior_summary #Rhat = 1.00, ESS > 1300
brm_p_task$pp_checks

brm_p_task$mcmc_trace
brm_p_task$mcmc_rank

parnames(brm_p_task$posterior_model)

plot(hypothesis(brm_p_task$posterior_model,"disorderasd:task_typefreemonologicalproduction = 0"))
plot(hypothesis(brm_p_task$posterior_model,"disorderasd:task_typesocialinteraction = 0"))
plot(hypothesis(brm_p_task$posterior_model,"disorderrhd:task_typeconstrainedproduction = 0"))
plot(hypothesis(brm_p_task$posterior_model,"disorderscz:task_typeconstrainedproduction = 0"))

plot(hypothesis(brm_p_task$posterior_model, "Intercept:disorderasd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_p_task$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_p_task$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "study_disorder"))

plot(hypothesis(brm_p_task$posterior_model, "Intercept:disorderasd = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_p_task$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_p_task$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "same_sample"))

plot(hypothesis(brm_p_task$posterior_model, "Intercept:disorderasd = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_p_task$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_p_task$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "expt_unique_dis"))

plot(hypothesis(brm_p_task$posterior_model, "nu = 0", class = ""))


# brm_pd_language ()
brm_p_language$posterior_summary #Rhat = 1.00, ESS > 1900
brm_p_language$pp_checks

brm_p_language$mcmc_trace
brm_p_language$mcmc_rank

parnames(brm_p_language$posterior_model)

plot(hypothesis(brm_p_language$posterior_model,"disorderasd:native_languageDanish = 0"))
plot(hypothesis(brm_p_language$posterior_model,"disorderasd:native_languageEnglish = 0"))
plot(hypothesis(brm_p_language$posterior_model,"disorderasd:native_languagePortuguese = 0"))
plot(hypothesis(brm_p_language$posterior_model,"disorderrhd:native_languageEnglish = 0"))
plot(hypothesis(brm_p_language$posterior_model,"disorderscz:native_languageEnglish = 0"))

plot(hypothesis(brm_p_language$posterior_model, "Intercept:disorderasd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_p_language$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_p_language$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "study_disorder"))

plot(hypothesis(brm_p_language$posterior_model, "Intercept:disorderasd = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_p_language$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_p_language$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "same_sample"))

plot(hypothesis(brm_p_language$posterior_model, "Intercept:disorderasd = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_p_language$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_p_language$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "expt_unique_dis"))

plot(hypothesis(brm_p_language$posterior_model, "nu = 0", class = ""))
```
Pitch (extra models)
```{r}
# brm_pd_task_no_by_no_by ()
brm_p_task_no_by$posterior_summary #Rhat = 1.00, ESS > 1200
brm_p_task_no_by$pp_checks

brm_p_task_no_by$mcmc_trace
brm_p_task_no_by$mcmc_rank

parnames(brm_p_task_no_by$posterior_model)

plot(hypothesis(brm_p_task_no_by$posterior_model,"disorderasd:task_typefreemonologicalproduction = 0"))
plot(hypothesis(brm_p_task_no_by$posterior_model,"disorderasd:task_typesocialinteraction = 0"))
plot(hypothesis(brm_p_task_no_by$posterior_model,"disorderrhd:task_typeconstrainedproduction = 0"))
plot(hypothesis(brm_p_task_no_by$posterior_model,"disorderscz:task_typeconstrainedproduction = 0"))

plot(hypothesis(brm_p_task_no_by$posterior_model, "Intercept = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_p_task_no_by$posterior_model, "Intercept = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_p_task_no_by$posterior_model, "Intercept = 0", class = "sd", group = "expt_unique_dis"))

plot(hypothesis(brm_p_task_no_by$posterior_model, "nu = 0", class = ""))

# brm_pd_language2 ()
brm_p_language2$posterior_summary #Rhat = 1.00, ESS > 2100
brm_p_language2$pp_checks

brm_p_language2$mcmc_trace
brm_p_language2$mcmc_rank

parnames(brm_p_language2$posterior_model)

plot(hypothesis(brm_p_language2$posterior_model,"disorderasd:native_languageDanish = 0"))
plot(hypothesis(brm_p_language2$posterior_model,"disorderasd:native_languageEnglish = 0"))
plot(hypothesis(brm_p_language2$posterior_model,"disorderasd:native_languagePortuguese = 0"))
plot(hypothesis(brm_p_language2$posterior_model,"disorderrhd:native_languageEnglish = 0"))
plot(hypothesis(brm_p_language2$posterior_model,"disorderscz:native_languageEnglish = 0"))

plot(hypothesis(brm_p_language2$posterior_model, "Intercept:disorderasd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_p_language2$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_p_language2$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "study_disorder"))

plot(hypothesis(brm_p_language2$posterior_model, "Intercept:dis_langasdDanish = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_p_language2$posterior_model, "Intercept:dis_langasdEnglish = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_p_language2$posterior_model, "Intercept:dis_langasdPortuguese = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_p_language2$posterior_model, "Intercept:dis_langrhdEnglish = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_p_language2$posterior_model, "Intercept:dis_langsczEnglish = 0", class = "sd", group = "same_sample"))

plot(hypothesis(brm_p_language2$posterior_model, "Intercept:dis_langasdDanish = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_p_language2$posterior_model, "Intercept:dis_langasdEnglish = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_p_language2$posterior_model, "Intercept:dis_langasdPortuguese = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_p_language2$posterior_model, "Intercept:dis_langrhdEnglish = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_p_language2$posterior_model, "Intercept:dis_langsczEnglish = 0", class = "sd", group = "expt_unique_dis"))

plot(hypothesis(brm_p_language2$posterior_model, "nu = 0", class = ""))


# brm_pd_language_no_by ()
brm_p_language_no_by$posterior_summary #Rhat = 1.00, ESS > 1500
brm_p_language_no_by$pp_checks

brm_p_language_no_by$mcmc_trace
brm_p_language_no_by$mcmc_rank

parnames(brm_p_language_no_by$posterior_model)

plot(hypothesis(brm_p_language2$posterior_model,"disorderasd:native_languageDanish = 0"))
plot(hypothesis(brm_p_language2$posterior_model,"disorderasd:native_languageEnglish = 0"))
plot(hypothesis(brm_p_language2$posterior_model,"disorderasd:native_languagePortuguese = 0"))
plot(hypothesis(brm_p_language2$posterior_model,"disorderrhd:native_languageEnglish = 0"))
plot(hypothesis(brm_p_language2$posterior_model,"disorderscz:native_languageEnglish = 0"))


plot(hypothesis(brm_p_language_no_by$posterior_model,"disorderasd:native_languageDanish = 0"))
plot(hypothesis(brm_p_language_no_by$posterior_model,"disorderasd:native_languageEnglish = 0"))
plot(hypothesis(brm_p_language_no_by$posterior_model,"disorderasd:native_languagePortuguese = 0"))
plot(hypothesis(brm_p_language_no_by$posterior_model,"disorderrhd:native_languageEnglish = 0"))
plot(hypothesis(brm_p_language_no_by$posterior_model,"disorderscz:native_languageEnglish = 0"))

plot(hypothesis(brm_p_language_no_by$posterior_model, "Intercept = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_p_language_no_by$posterior_model, "Intercept = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_p_language_no_by$posterior_model, "Intercept = 0", class = "sd", group = "expt_unique_dis"))

plot(hypothesis(brm_p_language_no_by$posterior_model, "nu = 0", class = ""))
```


Pitch variability
```{r}
# brm_pv_disorder (~ 0 + disorder)
brm_pv_disorder$posterior_summary #Rhat = 1.00, ESS > 1700
brm_pv_disorder$pp_checks

brm_pv_disorder$mcmc_trace
brm_pv_disorder$mcmc_rank

parnames(brm_pv_disorder$posterior_model)

plot(hypothesis(brm_pv_disorder$posterior_model,"disorderasd = 0"))
plot(hypothesis(brm_pv_disorder$posterior_model,"disorderlhd = 0"))
plot(hypothesis(brm_pv_disorder$posterior_model,"disorderrhd = 0"))
plot(hypothesis(brm_pv_disorder$posterior_model,"disorderscz = 0"))

plot(hypothesis(brm_pv_disorder$posterior_model, "Intercept:disorderasd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pv_disorder$posterior_model, "Intercept:disorderlhd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pv_disorder$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pv_disorder$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "study_disorder"))

plot(hypothesis(brm_pv_disorder$posterior_model, "Intercept:disorderasd = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pv_disorder$posterior_model, "Intercept:disorderlhd = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pv_disorder$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pv_disorder$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "same_sample"))

plot(hypothesis(brm_pv_disorder$posterior_model, "Intercept:disorderasd = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pv_disorder$posterior_model, "Intercept:disorderlhd = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pv_disorder$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pv_disorder$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "expt_unique_dis"))

plot(hypothesis(brm_pv_disorder$posterior_model, "nu = 0", class = "")) # WEIRD?


# brm_pv_task (~ 0 + disorder : task_type)
brm_pv_task$posterior_summary #Rhat = 1.00, ESS > 1300
brm_pv_task$pp_checks

brm_pv_task$mcmc_trace
brm_pv_task$mcmc_rank

parnames(brm_pv_task$posterior_model)

plot(hypothesis(brm_pv_task$posterior_model,"disorderasd:task_typeconstrainedproduction = 0"))
plot(hypothesis(brm_pv_task$posterior_model,"disorderasd:task_typefreemonologicalproduction = 0"))
plot(hypothesis(brm_pv_task$posterior_model,"disorderasd:task_typesocialinteraction = 0"))
plot(hypothesis(brm_pv_task$posterior_model,"disorderlhd:task_typeconstrainedproduction = 0"))
plot(hypothesis(brm_pv_task$posterior_model,"disorderrhd:task_typeconstrainedproduction = 0"))
plot(hypothesis(brm_pv_task$posterior_model,"disorderrhd:task_typefreemonologicalproduction = 0"))
plot(hypothesis(brm_pv_task$posterior_model,"disorderscz:task_typeconstrainedproduction = 0"))
plot(hypothesis(brm_pv_task$posterior_model,"disorderscz:task_typefreemonologicalproduction = 0"))
plot(hypothesis(brm_pv_task$posterior_model,"disorderscz:task_typesocialinteraction = 0"))

plot(hypothesis(brm_pv_task$posterior_model, "Intercept:disorderasd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pv_task$posterior_model, "Intercept:disorderlhd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pv_task$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pv_task$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "study_disorder"))

plot(hypothesis(brm_pv_task$posterior_model, "Intercept:disorderasd = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pv_task$posterior_model, "Intercept:disorderlhd = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pv_task$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pv_task$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "same_sample"))

plot(hypothesis(brm_pv_task$posterior_model, "Intercept:disorderasd = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pv_task$posterior_model, "Intercept:disorderlhd = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pv_task$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pv_task$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "expt_unique_dis"))

plot(hypothesis(brm_pv_task$posterior_model, "nu = 0", class = ""))


# brm_pv_language ()
brm_pv_language$posterior_summary #Rhat = 1.00, ESS > 1400
brm_pv_language$pp_checks

brm_pv_language$mcmc_trace
brm_pv_language$mcmc_rank

parnames(brm_pv_language$posterior_model)

plot(hypothesis(brm_pv_language$posterior_model,"disorderasd:native_languageDanish = 0"))
plot(hypothesis(brm_pv_language$posterior_model,"disorderasd:native_languageEnglish = 0"))
plot(hypothesis(brm_pv_language$posterior_model,"disorderasd:native_languageJapanese = 0"))
plot(hypothesis(brm_pv_language$posterior_model,"disorderasd:native_languagePortuguese = 0"))
plot(hypothesis(brm_pv_language$posterior_model,"disorderlhd:native_languageEnglish = 0"))
plot(hypothesis(brm_pv_language$posterior_model,"disorderlhd:native_languageKorean = 0"))
plot(hypothesis(brm_pv_language$posterior_model,"disorderrhd:native_languageEnglish = 0"))
plot(hypothesis(brm_pv_language$posterior_model,"disorderrhd:native_languageKorean = 0"))
plot(hypothesis(brm_pv_language$posterior_model,"disorderrhd:native_languagePolish = 0"))
plot(hypothesis(brm_pv_language$posterior_model,"disorderrhd:native_languageThai = 0"))
plot(hypothesis(brm_pv_language$posterior_model,"disorderscz:native_languageEnglish = 0"))

plot(hypothesis(brm_pv_language$posterior_model, "Intercept:disorderasd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pv_language$posterior_model, "Intercept:disorderlhd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pv_language$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pv_language$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "study_disorder"))

plot(hypothesis(brm_pv_language$posterior_model, "Intercept:disorderasd = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pv_language$posterior_model, "Intercept:disorderlhd = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pv_language$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pv_language$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "same_sample"))

plot(hypothesis(brm_pv_language$posterior_model, "Intercept:disorderasd = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pv_language$posterior_model, "Intercept:disorderlhd = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pv_language$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pv_language$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "expt_unique_dis"))

plot(hypothesis(brm_pv_language$posterior_model, "nu = 0", class = ""))
```
Pitch variability (extra models)
```{r}
# brm_pd_task_no_by_no_by ()
brm_pv_task_no_by$posterior_summary #Rhat =< 1.01, ESS > 899
brm_pv_task_no_by$pp_checks

brm_pv_task_no_by$mcmc_trace
brm_pv_task_no_by$mcmc_rank

parnames(brm_pv_task_no_by$posterior_model)

plot(hypothesis(brm_pv_task_no_by$posterior_model,"disorderasd:task_typeconstrainedproduction = 0"))
plot(hypothesis(brm_pv_task_no_by$posterior_model,"disorderasd:task_typefreemonologicalproduction = 0"))
plot(hypothesis(brm_pv_task_no_by$posterior_model,"disorderasd:task_typesocialinteraction = 0"))
plot(hypothesis(brm_pv_task_no_by$posterior_model,"disorderlhd:task_typeconstrainedproduction = 0"))
plot(hypothesis(brm_pv_task_no_by$posterior_model,"disorderrhd:task_typeconstrainedproduction = 0"))
plot(hypothesis(brm_pv_task_no_by$posterior_model,"disorderrhd:task_typefreemonologicalproduction = 0"))
plot(hypothesis(brm_pv_task_no_by$posterior_model,"disorderscz:task_typeconstrainedproduction = 0"))
plot(hypothesis(brm_pv_task_no_by$posterior_model,"disorderscz:task_typefreemonologicalproduction = 0"))
plot(hypothesis(brm_pv_task_no_by$posterior_model,"disorderscz:task_typesocialinteraction = 0"))

plot(hypothesis(brm_pv_task_no_by$posterior_model, "Intercept = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pv_task_no_by$posterior_model, "Intercept = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pv_task_no_by$posterior_model, "Intercept = 0", class = "sd", group = "expt_unique_dis"))

plot(hypothesis(brm_pv_task_no_by$posterior_model, "nu = 0", class = ""))

# brm_pv_language2 ()
brm_pv_language2$posterior_summary #Rhat = 1.00, ESS > 1600
brm_pv_language2$pp_checks

brm_pv_language2$mcmc_trace
brm_pv_language2$mcmc_rank

parnames(brm_pv_language2$posterior_model)

plot(hypothesis(brm_pv_language2$posterior_model,"disorderasd:native_languageDanish = 0"))
plot(hypothesis(brm_pv_language2$posterior_model,"disorderasd:native_languageEnglish = 0"))
plot(hypothesis(brm_pv_language2$posterior_model,"disorderasd:native_languageJapanese = 0"))
plot(hypothesis(brm_pv_language2$posterior_model,"disorderasd:native_languagePortuguese = 0"))
plot(hypothesis(brm_pv_language2$posterior_model,"disorderlhd:native_languageEnglish = 0"))
plot(hypothesis(brm_pv_language2$posterior_model,"disorderlhd:native_languageKorean = 0"))
plot(hypothesis(brm_pv_language2$posterior_model,"disorderrhd:native_languageEnglish = 0"))
plot(hypothesis(brm_pv_language2$posterior_model,"disorderrhd:native_languageKorean = 0"))
plot(hypothesis(brm_pv_language2$posterior_model,"disorderrhd:native_languagePolish = 0"))
plot(hypothesis(brm_pv_language2$posterior_model,"disorderrhd:native_languageThai = 0"))
plot(hypothesis(brm_pv_language2$posterior_model,"disorderscz:native_languageEnglish = 0"))

plot(hypothesis(brm_pv_language2$posterior_model, "Intercept:disorderasd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pv_language2$posterior_model, "Intercept:disorderlhd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pv_language2$posterior_model, "Intercept:disorderrhd = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pv_language2$posterior_model, "Intercept:disorderscz = 0", class = "sd", group = "study_disorder"))

plot(hypothesis(brm_pv_language2$posterior_model, "Intercept:dis_langasdDanish = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pv_language2$posterior_model, "Intercept:dis_langasdEnglish = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pv_language2$posterior_model, "Intercept:dis_langasdJapanese = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pv_language2$posterior_model, "Intercept:dis_langasdPortuguese = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pv_language2$posterior_model, "Intercept:dis_langlhdEnglish = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pv_language2$posterior_model, "Intercept:dis_langlhdKorean = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pv_language2$posterior_model, "Intercept:dis_langrhdEnglish = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pv_language2$posterior_model, "Intercept:dis_langrhdKorean = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pv_language2$posterior_model, "Intercept:dis_langrhdPolish = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pv_language2$posterior_model, "Intercept:dis_langrhdThai = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pv_language2$posterior_model, "Intercept:dis_langsczEnglish = 0", class = "sd", group = "same_sample"))

plot(hypothesis(brm_pv_language2$posterior_model, "Intercept:dis_langasdDanish = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pv_language2$posterior_model, "Intercept:dis_langasdEnglish = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pv_language2$posterior_model, "Intercept:dis_langasdJapanese = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pv_language2$posterior_model, "Intercept:dis_langasdPortuguese = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pv_language2$posterior_model, "Intercept:dis_langlhdEnglish = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pv_language2$posterior_model, "Intercept:dis_langlhdKorean = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pv_language2$posterior_model, "Intercept:dis_langrhdEnglish = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pv_language2$posterior_model, "Intercept:dis_langrhdKorean = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pv_language2$posterior_model, "Intercept:dis_langrhdPolish = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pv_language2$posterior_model, "Intercept:dis_langrhdThai = 0", class = "sd", group = "expt_unique_dis"))
plot(hypothesis(brm_pv_language2$posterior_model, "Intercept:dis_langsczEnglish = 0", class = "sd", group = "expt_unique_dis"))

plot(hypothesis(brm_pv_language2$posterior_model, "nu = 0", class = ""))


# brm_pv_language_no_by ()
brm_pv_language_no_by$posterior_summary #Rhat =< 1.01, ESS > 900
brm_pv_language_no_by$pp_checks

brm_pv_language_no_by$mcmc_trace
brm_pv_language_no_by$mcmc_rank

parnames(brm_pv_language_no_by$posterior_model)

plot(hypothesis(brm_pv_language_no_by$posterior_model,"disorderasd:native_languageDanish = 0"))
plot(hypothesis(brm_pv_language_no_by$posterior_model,"disorderasd:native_languageEnglish = 0"))
plot(hypothesis(brm_pv_language_no_by$posterior_model,"disorderasd:native_languagePortuguese = 0"))
plot(hypothesis(brm_pv_language_no_by$posterior_model,"disorderrhd:native_languageEnglish = 0"))
plot(hypothesis(brm_pv_language_no_by$posterior_model,"disorderscz:native_languageEnglish = 0"))

plot(hypothesis(brm_pv_language_no_by$posterior_model, "Intercept = 0", class = "sd", group = "study_disorder"))
plot(hypothesis(brm_pv_language_no_by$posterior_model, "Intercept = 0", class = "sd", group = "same_sample"))
plot(hypothesis(brm_pv_language_no_by$posterior_model, "Intercept = 0", class = "sd", group = "expt_unique_dis"))

plot(hypothesis(brm_pv_language_no_by$posterior_model, "nu = 0", class = ""))
```



# Model comparisons (both for pause duration, pitch, pitch variability)
```{r}
# Pause duration
# Comparing loo
loo_compare(brm_pd_disorder$posterior_model, brm_pd_task$posterior_model) # task
#loo_compare(brm_pd_disorder$posterior_model, brm_pd_language$posterior_model)

# Model weights
loo_model_weights(brm_pd_disorder$posterior_model, brm_pd_task$posterior_model) # task
#loo_model_weights(brm_pd_disorder$posterior_model, brm_pd_language$posterior_model)

# Pitch
# Comparing loo
loo_compare(brm_p_disorder$posterior_model, brm_p_task$posterior_model) # disorder, but big se
#loo_compare(brm_p_disorder$posterior_model, brm_p_language$posterior_model)

# Model weights
loo_model_weights(brm_p_disorder$posterior_model, brm_p_task$posterior_model) # task
#loo_model_weights(brm_p_disorder$posterior_model, brm_p_language$posterior_model)

# Pitch variability
# Comparing loo
loo_compare(brm_pv_disorder$posterior_model, brm_pv_task$posterior_model) # task
#loo_compare(brm_pv_disorder$posterior_model, brm_pv_language$posterior_model)

# Model weights
loo_model_weights(brm_pv_disorder$posterior_model, brm_pv_task$posterior_model) # task
#loo_model_weights(brm_pv_disorder$posterior_model, brm_pv_language$posterior_model)
```









#Hypothesis testing: ~ 0 + disorder
brm_pd_disorder, brm_p_disorder, brm_pv_disorder
```{r}
# conditional_effects(pause_duration_main_task_type$model, "")
# conditional_effects(pitch_main_task_type$model, "")
# conditional_effects(pitch_variability_main_task_type$model, "")

# Pause duration
hypothesis(pause_duration$model,"disorderscz > disorderlhd") # ER = 9.09
hypothesis(pause_duration$model,"disorderscz > disorderrhd") # ER = 125.98
hypothesis(pause_duration$model,"disorderlhd > disorderrhd") # ER = 6.66

hypothesis(pause_duration$model,"disorderscz > 0") # ER = 65.67

# Pitch
hypothesis(pitch$model,"disorderrhd > disorderasd") # ER = 0.96
hypothesis(pitch$model,"disorderrhd > disorderscz") # ER = 1.37
hypothesis(pitch$model,"disorderasd > disorderscz") # ER = 3.19

# Pitch variability
hypothesis(pitch_variability$model,"disorderasd > disorderrhd") # ER = 132.33
hypothesis(pitch_variability$model,"disorderasd > disorderlhd") # ER = 30.87
hypothesis(pitch_variability$model,"disorderasd > disorderscz") # ER = 420.05
hypothesis(pitch_variability$model,"disorderrhd > disorderlhd") # ER = 1.3
hypothesis(pitch_variability$model,"disorderrhd > disorderscz") # ER = 3.11
hypothesis(pitch_variability$model,"disorderlhd > disorderscz") # ER = 1.86

hypothesis(pitch_variability$model,"disorderasd > 0") # ER = Inf

# Remember: ASD = children, that might explain higher variability in pitch.
# Remember: ASD = might be more men/boys - at this age, do they still have a high pitch, or is that lower that women's?
```

# Hypothesis testing: ~ 0 + disorder + disorder : task
brm_pd_task, brm_p_task, brm_pv_task
```{r}
# samples <- posterior_samples(xx$model, pars = "bsp_momo_task_type")
# bayestestR::describe_posterior(samples)

# conditional_effects(brm_pd_task$model, "disorder:mo_task_type")
# conditional_effects(brm_p_task$model, "disorder:mo_task_type")
# conditional_effects(brm_pv_task$model, "disorder:mo_task_type")
```

# Hypothesis testing: ~ 0 + disorder + disorder : native_language
brm_pd_language, brm_p_language, brm_pv_language
```{r}
# conditional_effects(brm_pd_language$model, "disorder:native_language")
# conditional_effects(brm_p_language$model, "disorder:native_language")
# conditional_effects(brm_pv_language$model, "disorder:native_language")

#hypothesis...
```

Simo plots
```{r}
# plot(hypothesis(brm_pd_task$posterior_model, "disorderlhd:momo_task_type1[1] = 0", class = "simo"))
# plot(hypothesis(brm_pd_task$posterior_model, "disorderlhd:momo_task_type1[2] = 0", class = "simo"))
# plot(hypothesis(brm_pd_task$posterior_model, "disorderrhd:momo_task_type1[1] = 0", class = "simo"))
# plot(hypothesis(brm_pd_task$posterior_model, "disorderrhd:momo_task_type1[2] = 0", class = "simo"))
# plot(hypothesis(brm_pd_task$posterior_model, "disorderscz:momo_task_type1[1] = 0", class = "simo"))
# plot(hypothesis(brm_pd_task$posterior_model, "disorderscz:momo_task_type1[2] = 0", class = "simo"))
```

